### 2022-08-03 doc/TrashData.tex
Fixed issues from Gloria's 8/2 email. Added '$' to Prices in Table 2, added table reference for table 2. Changed 'WM_ADS' to 'WM-ADS' in figures and tables. Creaetd a new version of figure 6 that includes upstream merger only results.

\caption{\label{tab:}Republic/Santek Merger Simulation Inputs}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{llrrrrr}
\toprule
Disposal Firm & Collection Firm & Volume (000s) & Disposal Price & Disposal Margin (\$) & Collection Margin (\$) & Collection Price\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
Santek & Republic & 34 & 36 & 20 &  & 173\\
Santek & Santek & 218 & 16 & 0 &  & 134\\
Santek & WM\_ADS & 30 & 36 & 20 &  & 221\\
Santek & Regional & 30 & 36 & 20 &  & 221\\
\addlinespace
WasteConn & Republic & 19 & 25 & 14 &  & 162\\
WasteConn & WasteConn & 48 & 11 & 0 &  & 110\\
WasteConn & WM\_ADS & 17 & 25 & 14 &  & 210\\
WasteConn & Regional & 17 & 25 & 14 &  & 210\\
\bottomrule
\end{tabular}}
\end{table}

>>>>

\caption{\label{tab:trashdata}Republic/Santek Merger Simulation Inputs}
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}[t]{rrccccc}
\toprule
Disposal Firm & Collection Firm & Volume (000s) & Disposal Price (\$) & Disposal Margin (\$) & Collection Margin (\$) & Collection Price (\$)\\
\midrule
Republic & Republic & 165 & 42 & 0 & 44 & 179\\
\cmidrule{1-7}
 & Republic & 34 & 36 & 20 &  & 173\\

 & Santek & 218 & 16 & 0 &  & 134\\

 & WM-ADS & 30 & 36 & 20 &  & 221\\

\multirow{-4}{*}{\raggedleft\arraybackslash Santek} & Regional & 30 & 36 & 20 &  & 221\\
\cmidrule{1-7}
 & Republic & 19 & 25 & 14 &  & 162\\

 & WasteConn & 48 & 11 & 0 &  & 110\\

 & WM-ADS & 17 & 25 & 14 &  & 210\\

\multirow{-4}{*}{\raggedleft\arraybackslash WasteConn} & Regional & 17 & 25 & 14 &  & 210\\
\bottomrule
\end{tabular}}
\end{table}

### 2022-08-03 doc/VerticalArrangements.tex
Fixed issues from Gloria's 8/2 email. Added '$' to Prices in Table 2, added table reference for table 2. Changed 'WM_ADS' to 'WM-ADS' in figures and tables. Creaetd a new version of figure 6 that includes upstream merger only results.

Given these data sources, we construct our final input data set, as seen in Table 2.  As discussed above, we need to make several simplifying assumptions in order to transform the available information into the data required for our model.  We expect that the DOJ would have had access to more accurate confidential information during their investigation.  Therefore, we view our results as only illustrative of the types of analysis and results that could have been produced for this case.  Note that, other than imposing that Republic only offers disposal to itself, we do not structurally incorporate capacity constraints into the simulation model. We assume that the changes in volume that would be caused by the merger would be large enough to shift which constraints would be binding.

@@

Overall, the merger between Republic and Santek is estimated to lower upstream prices by 2.8\% and increase downstream prices by 12\%, resulting in \$16 million of annual harm to consumers and total annual producer benefits of approximately \$13.4 million. Thus, on net the model predicts the merger would be harmful despite the presence of significant EDM that reduces prices upstream.\footnote{Our calibrated bargaining parameters for retailers against Santek (1) and Republic (0.7) give a substantial edge to downstream firms, which, based on our analysis of the previous section, suggests consumers are likely to be harmed.  High bargaining power parameters are needed to explain the high collection margin compared to the disposal margin.  (See Table 2.)}  These effects are illustrated in more detail in Figure \ref{fig:TrashSimsFirms}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables and Figures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\small{\include{sumtable}}
\caption{Summary Statistics for Numerical Simulations}
\label{tab:simsum}
\end{table}

>>>>

Given these data sources, we construct our final input data set, as seen in Table \ref{tab:trashdata}.  As discussed above, we need to make several simplifying assumptions in order to transform the available information into the data required for our model.  We expect that the DOJ would have had access to more accurate confidential information during their investigation.  Therefore, we view our results as only illustrative of the types of analysis and results that could have been produced for this case.  Note that, other than imposing that Republic only offers disposal to itself, we do not structurally incorporate capacity constraints into the simulation model. We assume that the changes in volume that would be caused by the merger would be large enough to shift which constraints would be binding.

@@

Overall, the merger between Republic and Santek is estimated to lower upstream prices by 2.8\% and increase downstream prices by 12\%, resulting in \$16 million of annual harm to consumers and total annual producer benefits of approximately \$13.4 million. Thus, on net the model predicts the merger would be harmful despite the presence of significant EDM that reduces prices upstream.\footnote{Our calibrated bargaining parameters for retailers against Santek (1) and Republic (0.7) give a substantial edge to downstream firms, which, based on our analysis of the previous section, suggests consumers are likely to be harmed.  High bargaining power parameters are needed to explain the high collection margin compared to the disposal margin.  (See Table \ref{tab:trashdata}.)}  These effects are illustrated in more detail in Figure \ref{fig:TrashSimsFirms}.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Tables and Figures
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{table}
\caption{Summary Statistics for Numerical Simulations}
\label{tab:simsum}
\small{\include{sumtable}}
\end{table}
